---
title: "Workshop Candy Trade"
output:
  html_document:
    df_print: paged
---

```{r, load_packages}
library(rmarkdown)
library(ggplot2)
library(knitr)
```

This notebook contains all data and code to replicate our workshop candy trade analyses. Every participant of the workshop received a handful of candy. They then conducted an experiment exploring the impact of candy trading on their candy selection happiness:

1. **Pre-trade**: Participants were asked to rate the happiness of their candy selection on a scale from 1-10 (trade 0). 

2. **Trade 1**: Participants were then allowed to trade with one participant and rate the happiness with their selection following the trade on a scale from 1-10 (trade 1). 

3. **Trade 2**: Participants were then allowed to trade with the whole group and rate their happiness with their final selection on a scale from 1-10 (trade 2).

Our data was collected using a [google form](https://goo.gl/forms/Mxi2fKrOYc9UCB9j1). For each trade, the participants contributed their name (*"participant_name"*), which trade they had just finished (*"trade_number"*), and their current happiness with their candy selection (*"happiness_rating"*). 

```{r, echo=FALSE}
data <- read.csv("../data/data.csv", header=TRUE, sep=",", as.is=TRUE)
```

## Happiness rating vs. number of trades

To explore the trends in individual candy selection happiness over the trades, we created a simple line plot.
```{r, echo=TRUE}
myPlot = ggplot(data, aes(data$trade_number, 
    data$happiness_rating,colour=data$participant_name)) + 
    geom_line() + 
    geom_point()
plot(myPlot)
```

## Changes in candy selection happiness of our workshop group

Finally, we explored whether happiness changed significantly as a group over the trades using a boxplot.

```{r, echo=TRUE}
boxplot(happiness_rating ~ trade_number, data = data)
```
